Bipartite Fidelity and Loschmidt Echo of Bosonic Conformal Interface

### 2017-05-22 intro.tex
[draft] abstract and structure of paper added

% structure of the paper.
\todo[inline]{structure of the paper}

>>>>

The rest of the paper is organized as follows.

In Sec.~\ref{sec:bosonic_conformal_interface}, we introduce the general formalism for permeable interface and its lattice realization.

In Sec.~\ref{sec:analytic_numerics}, we analytically evaluate the free energy associated with fidelity and Loschmidt echo, and present the numerical results for comparison. We discuss our results and related experimental works in Sec.~\ref{sec:disc}. Finally we conclude in Sec.~\ref{sec:conclusion}.

In App.~\ref{app:F_correction}, we point out two corrections to the free energy, namely boundary logarithmic term and Schwarzian term. We derive the scale invariant interface for free bosonic lattice in App.~\ref{app:interface_free_boson}. The details of numerical simulation is presented in App.~\ref{app:comp_fid_echo}. In App.~\ref{app:pf_of_id}, we prove one identity that will be used repeatedly in the analytical evaluation. We calculate the free energy of one particular setup as an example in App.~\ref{app:gnd_dn_lambda}. The result is generalized to arbitrary boundary conditions in App.~\ref{app:lambda_12}. Throughout this paper, we work exclusively with the oscillator modes of free bosons. In App.~\ref{app:compact_diff_boson}, it is shown that the winding modes of compactified bosons will \emph{not} have contribution to the free energy at the leading order. Therefore the results presented in this paper remain valid in the more general case where two compactified bosons of different radii are connected by a conformal interface.
